### 2013-11-22 tests_Housing.Rmd
add datapoints: optimizing with less steps

```{r}
set.seed(204)

@@

source("gapolyfuncs.R")
report <- test.regularization(my.data, population=300, iterations=100, lambda=0.8, runs=25)

save(report, file="Housing300_lambda0.8.vs.no.reg_3.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300_lambda0.8.vs.no.reg_3.txt")

>>>>

```{r}
set.seed(304)

@@

source("gapolyfuncs.R")
report <- test.regularization(my.data, population=150, iterations=75, lambda=0.8, runs=50)

save(report, file="Housing300_lambda0.8.vs.no.reg_pop200.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300_lambda0.8.vs.no.reg_pop200.txt")
